05-conclusiones

### 2024-06-11 05-conclusiones.qmd
update discusion

Our research aimed to examine the relationship between the perception of meritocracy and the justification of market justice preferences among eighth-grade students in Chile. Overall, our findings provided mixed evidence regarding our hypotheses. While we found support for some associations, others did not align with our initial expectations. Hypothesis H1a posited that students who perceive greater meritocracy in society would show stronger preferences for market justice. The results confirm this hypothesis, indicating a positive relationship between the perception that talent and effort are rewarded in society and the preferences for market justice in access to services such as health, education, and pensions. This finding aligns with previous research suggesting that individuals who believe in a meritocratic system are more likely to justify social inequalities [@batruch_belief_2022; @wiederkehr_belief_2015]. Hypothesis H1b asserted that students who perceive greater meritocracy in school would show stronger preferences for market justice. The results show a mixed effect. The perception that talent is important for achieving good grades in school is associated with a greater preference for market justice in access to social services. Still, the perception that effort is important is associated with less preference for market justice. This highlights the influence of the school environment in shaping attitudes toward market justice, suggesting that meritocratic experiences in school can translate to broader societal views [@resh_sense_2010; @resh_sense_2014].

>>>>

Our research aimed to examine the relationship between the perception of meritocracy and the justification of market justice preferences among eighth-grade students in Chile. Overall, our findings provided mixed evidence regarding our hypotheses. While we found support for some associations, others did not align with our initial expectations. Hypothesis $H_{1a}$ posited that students who perceive greater meritocracy in society would show stronger preferences for market justice. The results support this hypothesis, indicating a positive relationship between the perception that talent and effort are rewarded in society and the preferences for market justice in access to services such as health, education, and pensions. This finding aligns with previous research suggesting that individuals who believe in a meritocratic system are more likely to justify social inequalities [@batruch_belief_2022; @wiederkehr_belief_2015]. Hypothesis H1b asserted that students who perceive greater meritocracy in school would show stronger preferences for market justice. The results show a mixed effect. The perception that talent is important for achieving good grades in school is associated with a greater preference for market justice in access to social services. Still, the perception that effort is important is associated with less preference for market justice. This highlights the influence of the school environment in shaping attitudes toward market justice, suggesting that meritocratic experiences in school can translate to broader societal views [@resh_sense_2010; @resh_sense_2014].
